OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-12-15 paper/response-to-reviewers.Rmd

---
output:
  pdf_document:
    latex_engine: xelatex
  github_document:
    html_preview: false
mainfont: "Helvetica"
fontsize: 12pt
geometry: margin=1.0in
---

### 2021-12-16 paper/paper.Rmd

We implemented the analysis workflow in Snakemake [@koster_snakemake_2012]
and wrote scripts in R [@r_core_team_r_2020],
Python [@van_rossum_python_2009],
and GNU bash [@noauthor_bash_nodate].
Software used includes mothur v1.47.0 [@schloss_introducing_2009],
VSEARCH v2.15.2 [@rognes_vsearch_2016],
the tidyverse metapackage [@wickham_welcome_2019],
R Markdown [@xie_r_2018],
ggraph [@pederson_ggraph_2021],
ggtext [@wilke_ggtext_2020],
numpy [@harris_array_2020],
the SRA toolkit [@noauthor_sra-tools_nodate],
and conda [@noauthor_anaconda_2016].
The complete workflow and supporting files required to reproduce this manuscript
are available at https://github.com/SchlossLab/Sovacool_OptiFit_2021.
<!-- TODO: update repo link with journal title -->

>>>>

We implemented the analysis workflow in Snakemake [@koster_snakemake_2012]
and wrote scripts in R [@r_core_team_r_2020],
Python [@van_rossum_python_2009],
and GNU bash [@noauthor_bash_nodate].
Software used includes mothur v1.47.0 [@schloss_introducing_2009],
VSEARCH v2.15.2 [@rognes_vsearch_2016],
the tidyverse metapackage [@wickham_welcome_2019],
R Markdown [@xie_r_2018],
ggraph [@pederson_ggraph_2021],
ggtext [@wilke_ggtext_2020],
numpy [@harris_array_2020],
the SRA toolkit [@noauthor_sra-tools_nodate],
and conda [@noauthor_anaconda_2016].
The complete workflow and supporting files required to reproduce this manuscript
are available at https://github.com/SchlossLab/Sovacool_OptiFit_mSphere_2022.
